### 2014-11-13 tex/intro.tex
reworked

@@

Importantly, the summary heap algorithm is sound and complete with
respect to properties that are provable using GSE. This proof is
accomplished by showing the existence of a bisimulation relation
between states in GSE and states in the summary heap algorithm. In
practical terms, any property that can be proved using GSE can also be
proved using summary heaps, furthermore, any property proved by
summary heaps can also be proved by GSE. Of course, Both require a bound on heap
reference chains and loops.

>>>>

In order to represent multiple heaps simultaneously in the context of
symbolic execution we define a novel heap representation and an
algorithm to initialize and update the heap on-the-fly. Our summary
heap approach supports aliasing, it does not require constraint
rewriting on heap updates, and it reduces the non-determinism in the
search space during symbolic execution.

\begin{comment}

@@

\end{comment}
We represent the heap as a bipartite graph consisting of references and locations. Each reference is able to point to multiple locations, where each edge is predicated on constraints over aliasing between references. Each location points to a single reference for a given field. The use of a bipartiate graph affords two
key advantages: (i) it allows for a non-recursive definition of objects which enables us to support aliasing, and (ii) it does not require rewriting of the constraints during updates to the heap nor does it introduce auxillary variables into the constraints.

This summary heap algorithm defines how the bipartite graph is updated during lazy initialization. Unlike GSE, however, the summary heap algorithm introduces non-determinism in the search only at points of divergence in the control flow graph. These points of non-determinism are at field accesses or writes that lead to null-pointer exceptions and at comparisons of references. The former represents a divergence due to exceptional control flow while the latter is due to program structure. The precise heap representation based on a bipartiate graph coupled with this algorithm to perform updates to the heap enable us to successfully mitigate the state space explosion problem in GSE.

The summary heap algorithm is sound and complete with respect to
properties that are provable using GSE. This proof is accomplished by
showing the existence of a bisimulation relation between states in GSE
and states in the summary heap algorithm. In practical terms, any
property that can be proved using GSE can also be proved using summary
heaps, furthermore, any property proved by summary heaps can also be
proved by GSE. Of course, both require a bound on heap reference
chains and loops.
